### 2018-12-12 chapters/3-results.tex
figs

>>>>

\begin{figure}[!h]
    \centering \includegraphics[width=1.0\textwidth]{figures/fig3}
    \caption{{\bf An example of texture feature maps.}
    These are extracted from DWI parametric maps (ADCₘ, ADCₖ, K), T₂-weighted
    imaging (T₂w), and parametric map of T₂ relaxation values (T₂). Source image
    type, window size, and texture descriptor parameters are shown above the
    images. The two lesions are outlined; their Gleason scores are 4+3 (lower)
    and 3+4 (upper).}%
    \label{fig:tmap}
\end{figure}

\begin{figure}[!h]
    \centering \includegraphics[width=1.0\textwidth]{figures/fig4}
    \caption{{\bf ROC curves within each image type (T₂w, ADCₘ, ADCₖ, K, T₂).}
    A:~The best statistical feature. B:~The best texture feature. The final
    model of the best selected features from ADCₘ, K, and T₂w obtained using L1
    regularized logistic regression and validated with leave-pair-out
    cross-validation (LPOCV) is also included in both A and B.}%
    \label{fig:roc}
\end{figure}
